%-------------------------
% Resume in Latex
% Author : RAHUL S HOSKERI (rhoskeri50@gmail.com)
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{multirow}
\usepackage[T1]{fontenc}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-10pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------

    
\begin{center}
\begin{tabular}{c}
  \textbf{\Large RAHUL S HOSKERI}\\ 
\end{tabular}

 \begin{tabular}{l | c | r }
%  \hline
 \textit{ Email : \href{mailto:rhoskeri@ucmerced.edu}{rhoskeri@ucmerced.edu}} \hspace{1pt} & \hspace{1pt} \textit{Mobile: +1-628-800-4383} \hspace{1pt}  & \hspace{1pt}  \textit{GitHub: \href{https://github.com/Rahul664}{Rahul664}}\\
\end{tabular}
\end{center}
  


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University Of California, Merced}{Merced, CA}
      {Master of Science in Electrical Engineering and Computer Science;  GPA: 3.8/4.0}{Aug. 2019 -- Present (May. 2021)}
      \resumeItemListStart
        \resumeItem{Relevant Courses}
          {Advance Algorithm Design and Analysis, Parallel Computing, Advance Intelligent Systems, Distributed Computing, Computer Visison.}
     \resumeItemListEnd
    \resumeSubheading
      {Visvesvaraya Technological University}{Bengaluru,India}
      {Bachelor of Engineering in Computer Science and Engineering;  GPA: 3.45/4.0}{Aug. 2014 -- June. 2018}
         \resumeItemListStart
        \resumeItem{Relevant Courses}
          {Design and Analysis of Algorithm, Data Structures, Unix and Shell Programming, Object-Oriented Programming, Database Management Systems, Professional Ethics.}
     \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tracking Misplaced Items in the Autonomous Retail Store. (CPS-IoT Week 2020)}{}
      {Computer Vision $\vert$ Sensor Data Analysis $\vert$ Object Classification}{}
      \resumeItemListStart
        \resumeItem{Objective}
          {Using \textbf{\emph{multi modal sensor fusion technique}}, successfully classified the misplaced item with an accuracy of \textbf{70\%} in worst case scenarios and enhanced object classification.}

      \resumeItemListEnd

       \resumeSubheading
      {Optimizing High Performance Computing (HPC) Application Using Neural Network.}{}
      { High Performance Computing $\vert$ Neural Networks $\vert$ \url{https://github.com/Rahul664/OpenFuelCell}}{}
      \resumeItemListStart
        \resumeItem{Objective:}
          {Employing \textbf{multi layer perceptron neural network model} improved the performance of  solid oxide fuel cell application simulation by approximately \textbf{98\% from 120 minutes to 1.7 minutes}.}
      \resumeItemListEnd
        \resumeSubheading
      {Handwritten Optical Character Recognition.}{}
      {Cross Correlation Measure $\vert$\url{ https://github.com/Rahul664/OCR}}{}
      \resumeItemListStart
        \resumeItem{Objective:}
          {Used \textbf{Optical Character Recognistion (OCR) to recognise and translate tulu kannada to classical kannada characters}.}
         \resumeItem{}
         {Used Cross-Correlation algorithm for recognition and obtained \textbf{82.85\% accuracy}}
      \resumeItemListEnd
          \resumeSubheading
      {Facebook Messenger Weather Bot.}{}
      {Chat Bot $\vert$ Open Weather API $\vert$\url{ https://bit.ly/2xdBKl1}}{}
      \resumeItemListStart
        \resumeItem{Objective:}
          {Interact with user to fetch location and retrieve the weather at that location. Used \textbf{Open Weather map API with PhP curl HTML request, response with chat fuel bot platform}. This could be integrated as the Amazon Alexa skill.}
        % \resumeItem{}
        % {Used \textbf{Open Weather map API with PhP curl HTML request, response with chat fuel bot platform.} This could be integrated as the Amazon Alexa skill.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University Of California, Merced}{Merced, CA}
      {Research Assistant $\vert$ Sensor Data Analysis}{Jun 2020 - Present}
      \resumeItemListStart
        \resumeItem{Objective:}
          {"\textbf{\emph{Object Classification}} through feature comparison of plot, obtained from weight sensor data of an autonomous store  (AiFi)".}
      \resumeItemListEnd

       \resumeSubheading
      {University Of California, Merced}{Merced, CA}
      {Teaching Assistant $\vert$ Calculus $\vert$ Approximation}{Jan 2020 - May 2020}
      \resumeItemListStart
        \resumeItem{}
          {Teaching Calculus course, enhanced my understanding of the mathematical concepts used for machine learning like \textbf{\emph{approximation and optimization}} for real world problems.}
         \resumeItem{}
         {Responsible for tutoring, conducting quizzes and grading, which emphasises my \textbf{\emph{group management and coordinating skills}.}}
      \resumeItemListEnd
        \resumeSubheading
      {Wipro Technologies Ltd}{Bengaluru, India}
      {Project Engineer $\vert$ Business Data Analysis $\vert$ Data Interpretaion}{Jul 2018 - Jan 2019}
      \resumeItemListStart
        \resumeItem{Responsibilities:}
          {Worked for Marsh and McLennan insurance project, \textbf{\emph{analyzing the insurance report data}} using the SAP Business Objects to study the business growth and report to help make the business decsions.}
          \resumeItem{}
          {Implemented \textbf{\emph{Python script to clean csv file and convert to excel}} file for better readability and reduced the manual effort that was used before.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd



%--------PROGRAMMING SKILLS------------
\section{Programming Skills And Certifications}
 \resumeSubHeadingListStart
\item{C++, Python, Java.}
\item{\textbf{“Programming and Data Structure and Algorithm using Python”\\}
from Indian Institute of Technology, Madras (IITM) (NPTEL) \href{https://rb.gy/xch9er}{Reg No: NPTEL17CS28S2190163}}
 \resumeSubHeadingListEnd


%-------------------------------------------

\end{document}
